Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-03 Manuscript/proto-manuscript.tex
Some comments about stoichimetry issues added

\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure} \\
  \todo{We should run a simulation for the system withtout ions with the
    same (or close) temperature as the experimental data. The NMR data is at 300K
    so that would be good. I think that this would be also close enough for the scattering data at 303K.
  }
\end{figure}

@@

\todo{Put details of the cation-binding stoichiometry analysis to SI.}
\todo{Update the binding isotherm figure with new simulations}
\todo{SAMULI: The same authors have also literature, where they say that ternary complex may not
  be the only option. I will recheck and come back to this.}
\todo{SAMULI: I would also analyze how much there is contact between ions and different
parts of the lipid (phosphase, carbonyl, etc.).}
\todo{SAMULI: I think we should quantify this, i.e. how much there are these.
  Maybe also the other possible complexes? Maybe also the correlation betweem complexes
  and binding sites, if it is not too much work.
      JOE: This looks like a careful work for the next paper to me. 
           I'd only add a relatively simple analysis of binding sites and probably the propensity of 1-2-3 membered clusters.}. 
\todo{Finalize stoichiometry analysis for \ce{Na^+}, \ce{Ca^{2+}},
  their interaction energies with the lipid membrane, etc,
  and finalize the discussion after these results.}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17_q80_sig89.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure} \\
  \todo{We should run a simulation for the system withtout ions with the
    same (or close) temperature as the experimental data. The NMR data is at 300K
    so that would be good. I think that this would be also close enough for the scattering data at 303K.
  }
\end{figure}

@@

\todo{Put details of the cation-binding stoichiometry analysis to SI.} \\
\todo{Update the binding isotherm figure with new simulations} \\
\todo{SAMULI: The same authors have also literature, where they say that ternary complex may not
  be the only option. I will recheck and come back to this.
  SAMULI: This is written in \cite{macdonald87}:
  ''Ca2+binding to POPC bilayers over the whole concentration range can be best described in terms
  of formation of a ternary complex involving complexation of two lipids to one calcium ion (Altenbach and Seelig, 1984).
  The addition of a sodium competition term has not changed this conclusion. However, if Ca2+ concentrations
  up to 100 mM are considered, the data can be equally well explained by a 1:1 binding mechanism (cf. Figure 7).
  In contrast, the Ca2+ binding to POPC-POPG mixtures can be best described by assuming a 1:l stoichiometry regardless of the range of Ca2+concentrations.''
  We might or might not want to discuss about this.} \\
\todo{SAMULI: I would also analyze how much there is contact between ions and different
parts of the lipid (phosphase, carbonyl, etc.).} \\
\todo{SAMULI: I think we should quantify this, i.e. how much there are these.
  Maybe also the other possible complexes? Maybe also the correlation betweem complexes
  and binding sites, if it is not too much work.
  JOE: This looks like a careful work for the next paper to me. 
  I'd only add a relatively simple analysis of binding sites and probably the propensity of 1-2-3 membered clusters.
  SAMULI: I agree that we should not use too much time on this now.}. \\
\todo{Finalize stoichiometry analysis for \ce{Na^+}, \ce{Ca^{2+}},
  their interaction energies with the lipid membrane, etc,
  and finalize the discussion after these results.}
